A comparison of model-based and design-based approaches for spatial data.

### 2021-06-07 inst/SpatialDVM_Manuscript/SpatialDVM_Manuscript.Rmd

Several comparisons between model-based and design-based for spatial data have been considered, but they tend to compare spatial models to IRS (Independent Random Sampling) or SIRS (stratified IRS). No comparison has been made between spatial models and spatially balanced design-based approaches.

@@

>>>>

Several comparisons between modegitl-based and design-based for spatial data have been considered, but they tend to compare spatial models to IRS (Independent Random Sampling) or SIRS (stratified IRS). No comparison has been made between spatial models and spatially balanced design-based approaches.

@@

* wang2012spatial - sampling and inference steps, thorough overview in terms of spatial context, lots of references
